Optimal (Multiway) Spatial Joins

### 2024-05-26 msj.tex
yufei

\begin{figure}
    \includegraphics[height=23mm]{./artwork/guard}

    \figcapup
    \caption{Define 3-tuple $\bm{t} = \set{r_1, r_2, r_3}$. $B_\bm{t}$ is the rectangle in gray, $\gleft(\bm{t}) = r_3$ and $\gbot(\bm{t}) = r_2$.}
    \label{fig:guard}
    \figcapdown
\end{figure}

@@

\begin{figure}
    \begin{tabular}{cc}
        \includegraphics[height=27mm]{./artwork/type1} &
        \hspace{5mm} \includegraphics[height=27mm]{./artwork/type2} \\
        (a) Type 1 &
        (b) Type 2
    \end{tabular}

@@

@@

>>>>

\begin{figure}
    \includegraphics[height=27mm]{./artwork/guard}

    \figcapup
    \caption{Consider a 4-tuple $\bm{t} = \set{r_1, r_2, r_3, r_4}$. $B_\bm{t}$ is the rectangle in gray, $\gleft(\bm{t}) = r_3$ and $\gbot(\bm{t}) = r_2$.}
    \label{fig:guard}
    \figcapdown
\end{figure}

@@

\begin{figure}
    \begin{tabular}{cc}
        \includegraphics[height=23mm]{./artwork/type1} &
        \hspace{5mm} \includegraphics[height=27mm]{./artwork/type2} \\
        (a) Type 1 &
        (b) Type 2
    \end{tabular}

@@

\begin{figure}
    \begin{tabular}{cc}
        \includegraphics[height=27mm]{./artwork/cat1} &
        \hspace{5mm} \includegraphics[height=27mm]{./artwork/cat2} \\
        (a) Category 1 &
        (b) Category 2
    \end{tabular}

    \figcapup
    \caption{Classifying $k$-SJ result tuples ($k$ = 4)}
    \label{fig:ksj:cats}
    \figcapdown
\end{figure}

@@

This section will tackle the (generic form of the) $k$-SJ problem, where the input comprises $k$ sets of rectangles $R_1, R_2, ..., R_k$. The join result, denoted by $\J(R_1, R_2, ..., R_k)$, is the set of $k$-tuples $\bm{t} = (r_1, r_2, ..., r_k) \in R_1 \times R_2 \times ... \times R_k$ satisfying the condition that $B_\bm{t}$ --- defined as $\bigcap_{i=1}^k r_i \ne \emptyset$; see \eqref{eqn:B_t} --- is non-empty.

Consider any result tuple $\bm{t} \in \J(R_1, R_2, ..., R_k)$, and let $p$ be the top-left corner of $B_\bm{t}$. Depending on how $p$ is determined, we classify $\bm{t}$ into one of the two categories below: 
\myitems{
    \item {{\bf Cat.\ 1:}} $p$ is a corner of a rectangle $\bm{t}[i]$, for some $i \in [k]$.

    \item {{\bf Cat.\ 2:}} $p$ is not a corner of any of $\bm{t}[1], ..., \bm{t}[k]$. Note that this means $p$ must be the intersection point between the left edge of some rectangle $\bm{t}[i]$ and the top edge of another rectangle $\bm{t}[j]$, where $i, j \in [k]$ and $i \ne j$.
}
Figure~\ref{fig:ksj:cats} illustrates a tuple $\bm{t} = (r_1, r_2, ..., r_4)$ of each category.

We assume the existence of an algorithm $\A$ that can solve any $(k-1)$-SJ problem in $F_{k-1}(n, \out)$ time, where $n$ and $\out$ are the input and output sizes, respectively. Equipped with $\A$, we will find the result tuples of each category separately, within the time complexity stated in Theorem~\ref{thm:main-recur}.

\extraspacing {\bf Category 1.}
